---
title: "SDD's graphic"
description: |
  Article about Urchins
author:
  - name: Geerinckx Naomie
    url: https://guyliann.netlify.com/fr
date: 11-14-2020
categories:
  - "SDD"
  - "Urchin"
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
SciViews::R
```

```{r importation}
urchin <- read("urchin_bio", package = "data.io")
```

## Introduction :

In this article, I will talk about **integument of urchins**. The integument is the weight of the urchin without content of test. For that, I will show you a graphic about the dry integument of urchin in function of integument wether they live in nature or in farm.

## Graphic : 

```{r graphic}
ggplot(urchin, aes(integuments, dry_integuments, col = origin)) +
    geom_jitter() +
  labs(x = "Integuments [g]", y="Dry_integuments [g]")
````
## Conclusion:

On the graphic, we can see a correlation between integuments and dry integuments. Furthermore, we can deduce that the urchins of fishery have less water in their test. Finally, urchins of farm can reach an integument more elevated. That is logical because we saw in class that urchin coming from farm are heavier.


