---
title: "SDD's graphic"
description: |
  Article about Urchins
author:
  - name: Geerinckx Naomie
    url: https://guyliann.netlify.com/fr
date: 11-14-2020
categories:
  - "SDD"
  - "Urchin"
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
SciViews::R
```

```{r importation}
urchin <- read("urchin_bio", package = "data.io")
```

## Introduction :

In this article, I will talk about weight of **urchin's gonads**. For that, I will show you a graphic about the gonad's weight in different steps of maturity (step 0 where gonads are missing or depleted, step 1 where gonads are growing and step 2 where gonads are mature).

## Graphic : 

```{r graphic}

ggplot(urchin, aes(x = maturity, y = gonads, fill = maturity)) +
  geom_bar(stat = "Identity", width = 0.3) +
  labs(x= "Maturity", y = "Gonad's weight [g]")
```

## Conclusion:

I suppose the values for stade 0 are wrongs because we can not have a such high weight. In effect, at stade 0, gonads are either absents or spent. However (if we do not take values for stade 0), we can determinate a correlation with gonad's weight and maturity. The weight of gonads increases when the maturity of these enhances. 


